Supporting Information for ``Seniority and Hierarchy Configuration Interaction for Radicals and Excited States''

### 2023-10-22 Manuscript/sup.tex
saving work

\begin{table}[ht!]
\caption{Number of Determinants in Hierarchy-, Excitation, and Seniority-Based CI Routes, as well as in Full CI, for \ce{OH}, \ce{CN}, vinyl, and \ce{H7},
with the cc-pVDZ basis set and frozen-core approximation.}
\label{tab:ndet_open}
\begin{ruledtabular}
\begin{tabular}{lrrrr}
method &     \ce{OH} &         \ce{CN} &                 vinyl &     \ce{H7} \\
\hline
RHF    &           1 &               1 &                     1 &           1 \\
\hline
CIS    &         131 &             280 &                   533 &         221 \\
CISD   &       5 871 &          27 559 &               100 983 &      16 403 \\
CISDT  &     110 031 &       1 196 384 &             8 620 123 &     491 695 \\
CISDTQ &   1 035 501 &      27 468 434 &           397 093 838 &   7 015 800 \\
\hline
CIs1   &      58 140 &       8 288 280 &         1 160 068 104 &     209 440 \\
CIs3   &   1 686 060 &     530 449 920 &       143 268 410 844 &   9 948 400 \\
CIs5   &  12 267 540 &   9 233 143 920 &     4 974 952 064 004 & 107 338 000 \\
\hline
hCI1   &         299 &             658 &                 1 268 &         500 \\
hCI1.5 &       3 491 &          11 809 &                35 813 &      11 009 \\
hCI2   &      25 401 &         136 234 &               569 178 &      96 290 \\
hCI2.5 &     162 265 &       1 417 234 &             8 899 178 &     832 850 \\
hCI3   &     732 107 &      10 879 834 &           102 007 753 &   5 530 745 \\
hCI3.5 &   2 706 807 &      71 632 834 &         1 011 139 788 &  23 829 890 \\
hCI4   &   7 774 870 &     384 458 809 &         8 484 940 738 &  92 360 660 \\
\hline
FCI    &  45 070 128 & 446 075 229 600 & 4 672 770 853 882 482 & 342 696 200 \\
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}[ht!]
\caption{Number of Determinants in Hierarchy-, Excitation, and Seniority-Based CI Routes, as well as in Full CI, for \ce{H4}, \ce{N2}, \ce{F2}, \ce{HF}, \ce{H8}, and ethylene,
with the cc-pVDZ basis set and frozen-core approximation.}
\label{tab:ndet_closed}
\begin{ruledtabular}
\begin{tabular}{lrrr}
method & \ce{H4} &       \ce{N2} &         \ce{F2} \\
\hline
RHF    &       1 &             1 &               1 \\
\hline
CIS    &      73 &           211 &             267 \\
CISD   &   1 675 &        15 436 &          25 138 \\
CISDT  &  12 691 &       483 036 &       1 048 174 \\
CISDTQ &  36 100 &     7 745 886 &      23 236 165 \\
\hline
CIs0   &     190 &        65 780 &         657 800 \\
CIs2   &   7 030 &     6 972 680 &      88 145 200 \\
CIs4   &  36 100 &   145 110 680 &   2 450 305 000 \\
\hline
hCI1   &     109 &           316 &             400 \\
hCI1.5 &     757 &         2 836 &           3 592 \\
hCI2   &   3 052 &        34 336 &          57 457 \\
hCI2.5 &  17 740 &       311 536 &         531 469 \\
hCI3   &  36 100 &     1 913 836 &       4 209 850 \\
hCI3.5 &  36 100 &    11 489 836 &      28 628 650 \\
hCI4   &  36 100 &    49 045 711 &     153 775 000 \\
\hline
FCI    &  36 100 & 4 327 008 400 & 432 700 840 000 \\
\hline
\hline
& & & \\
\hline
\hline
method &    \ce{HF} &       \ce{H8} &           ethylene \\
\hline
RHF    &          1 &             1 &                  1 \\
\hline
CIS    &        113 &           289 &                409 \\
CISD   &      4 341 &        28 585 &             58 855 \\
CISDT  &     68 405 &     1 174 345 &          3 731 535 \\
CISDTQ &    531 595 &    23 805 835 &        124 764 480 \\
\hline
CIs0   &      3 060 &        91 390 &          3 838 380 \\
CIs2   &    174 420 &    13 251 550 &        786 867 900 \\
CIs4   &  1 845 180 &   358 705 750 &     33 086 835 600 \\
\hline
hCI1   &        169 &           433 &                613 \\
hCI1.5 &      1 065 &         5 905 &              8 365 \\
hCI2   &      9 255 &        62 605 &            134 590 \\
hCI2.5 &     55 119 &       879 085 &          1 952 230 \\
hCI3   &    227 109 &     5 659 525 &         17 306 800 \\
hCI3.5 &    856 101 &    40 616 965 &        163 795 120 \\
hCI4   &  2 216 460 &   213 974 380 &      1 112 401 240 \\
\hline
FCI    &  9 363 600 & 8 352 132 100 & 14 733 161 024 400 \\
\end{tabular}
\end{ruledtabular}
\end{table}

>>>>

\begin{table}[ht!]
\caption{\fk{Number of Determinants in Hierarchy-, Excitation, and Seniority-Based CI Routes, as well as in Full CI, for \ce{OH}, \ce{CN}, vinyl, and \ce{H7},
with the cc-pVDZ basis set and frozen-core approximation.}}
\label{tab:ndet_open}
{\color{orange}
\begin{ruledtabular}
\begin{tabular}{lrrrr}
method &     \ce{OH} &         \ce{CN} &                 vinyl &     \ce{H7} \\
\hline
RHF    &           1 &               1 &                     1 &           1 \\
\hline
CIS    &         131 &             280 &                   533 &         221 \\
CISD   &       5 871 &          27 559 &               100 983 &      16 403 \\
CISDT  &     110 031 &       1 196 384 &             8 620 123 &     491 695 \\
CISDTQ &   1 035 501 &      27 468 434 &           397 093 838 &   7 015 800 \\
\hline
CIs1   &      58 140 &       8 288 280 &         1 160 068 104 &     209 440 \\
CIs3   &   1 686 060 &     530 449 920 &       143 268 410 844 &   9 948 400 \\
CIs5   &  12 267 540 &   9 233 143 920 &     4 974 952 064 004 & 107 338 000 \\
\hline
hCI1   &         299 &             658 &                 1 268 &         500 \\
hCI1.5 &       3 491 &          11 809 &                35 813 &      11 009 \\
hCI2   &      25 401 &         136 234 &               569 178 &      96 290 \\
hCI2.5 &     162 265 &       1 417 234 &             8 899 178 &     832 850 \\
hCI3   &     732 107 &      10 879 834 &           102 007 753 &   5 530 745 \\
hCI3.5 &   2 706 807 &      71 632 834 &         1 011 139 788 &  23 829 890 \\
hCI4   &   7 774 870 &     384 458 809 &         8 484 940 738 &  92 360 660 \\
\hline
FCI    &  45 070 128 & 446 075 229 600 & 4 672 770 853 882 482 & 342 696 200 \\
\end{tabular}
\end{ruledtabular}
}
\end{table}

\begin{table}[ht!]
\caption{\fk{Number of Determinants in Hierarchy-, Excitation, and Seniority-Based CI Routes, as well as in Full CI, for \ce{H4}, \ce{N2}, \ce{F2}, \ce{HF}, \ce{H8}, and ethylene,
with the cc-pVDZ basis set and frozen-core approximation.}}
\label{tab:ndet_closed}
{\color{orange}
\begin{ruledtabular}
\begin{tabular}{lrrr}
method & \ce{H4} &       \ce{N2} &         \ce{F2} \\
\hline
RHF    &       1 &             1 &               1 \\
\hline
CIS    &      73 &           211 &             267 \\
CISD   &   1 675 &        15 436 &          25 138 \\
CISDT  &  12 691 &       483 036 &       1 048 174 \\
CISDTQ &  36 100 &     7 745 886 &      23 236 165 \\
\hline
CIs0   &     190 &        65 780 &         657 800 \\
CIs2   &   7 030 &     6 972 680 &      88 145 200 \\
CIs4   &  36 100 &   145 110 680 &   2 450 305 000 \\
\hline
hCI1   &     109 &           316 &             400 \\
hCI1.5 &     757 &         2 836 &           3 592 \\
hCI2   &   3 052 &        34 336 &          57 457 \\
hCI2.5 &  17 740 &       311 536 &         531 469 \\
hCI3   &  36 100 &     1 913 836 &       4 209 850 \\
hCI3.5 &  36 100 &    11 489 836 &      28 628 650 \\
hCI4   &  36 100 &    49 045 711 &     153 775 000 \\
\hline
FCI    &  36 100 & 4 327 008 400 & 432 700 840 000 \\
\hline
\hline
& & & \\
\hline
\hline
method &    \ce{HF} &       \ce{H8} &           ethylene \\
\hline
RHF    &          1 &             1 &                  1 \\
\hline
CIS    &        113 &           289 &                409 \\
CISD   &      4 341 &        28 585 &             58 855 \\
CISDT  &     68 405 &     1 174 345 &          3 731 535 \\
CISDTQ &    531 595 &    23 805 835 &        124 764 480 \\
\hline
CIs0   &      3 060 &        91 390 &          3 838 380 \\
CIs2   &    174 420 &    13 251 550 &        786 867 900 \\
CIs4   &  1 845 180 &   358 705 750 &     33 086 835 600 \\
\hline
hCI1   &        169 &           433 &                613 \\
hCI1.5 &      1 065 &         5 905 &              8 365 \\
hCI2   &      9 255 &        62 605 &            134 590 \\
hCI2.5 &     55 119 &       879 085 &          1 952 230 \\
hCI3   &    227 109 &     5 659 525 &         17 306 800 \\
hCI3.5 &    856 101 &    40 616 965 &        163 795 120 \\
hCI4   &  2 216 460 &   213 974 380 &      1 112 401 240 \\
\hline
FCI    &  9 363 600 & 8 352 132 100 & 14 733 161 024 400 \\
\end{tabular}
\end{ruledtabular}
}
\end{table}
